|

### 2025-01-22 doc/paper.qmd
revised section names

# List of Abbreviations
\setlength{\parindent}{0em}
**CRSP**: Center for Research in Security Prices  
**CQA**: Corporate Decision-Making and Quantitative Analysis  
**EC**: European Commission  
**EU**: European Union  
**IDE**: Integrated Development Environment  
**TREAT**: TRR 266 Template for Reproducible Empirical Accounting Research  
**UK**: United Kingdom  
**WRDS**: Wharton Research Data Services

@@

Building on these foundations, Assignment III investigates the informativeness of quarterly earnings announcements and their contribution to annual share price movements. The project replicates and extends @ball_how_2008, assessing the extent to which earnings releases serve as a source of new information for financial markets. By integrating multiple datasets from WRDS and applying an event-study methodology, this study evaluates the economic role of earnings disclosures in market efficiency. The integration of multiple databases adds complexity, requiring a detailed understanding of their structures and careful scripting to extract, align, and analyze data effectively. Key tasks include replicating and comparing original results, extending the analysis to data from 2007–2023, and applying the methodology to a non-U.S. country to explore cross-market variations.

@@

Earnings announcements provide investors with valuable information about a firm’s market value, with stock prices reacting significantly when earnings news deviates from expectations [@fink_review_2021, p.2]. The seminal study by @ball_empirical_1968 was the first to document this relationship, and over the past decades, more than a thousand studies have examined the interplay between capital markets and financial statements, a research stream that originated with Ball and Brown (1968) [@kothari_capital_2001]. This reinforces the role of earnings announcements as a crucial source of financial information.

@@

# Task 1 {#sec-task1}

@@

# Task 2 {#sec-task2}

# Task 3 {#sec-task3}

# Task 4 {#sec-task4}

>>>>

# List of Abbreviations
\setlength{\parindent}{0em}
**CRSP**: Center for Research in Security Prices  
**CQA**: Corporate Decision-Making and Quantitative Analysis  
**DV**: Dependent Variable
**IV**: Independent Variable
**EU**: European Union  ##
**IDE**: Integrated Development Environment  
**TREAT**: TRR 266 Template for Reproducible Empirical Accounting Research  
**UK**: United Kingdom  ##
**WRDS**: Wharton Research Data Services

@@

Building on these foundations, Assignment III investigates the informativeness of quarterly earnings announcements and their contribution to annual share price movements. The project replicates and extends @ball_how_2008, assessing the extent to which earnings releases serve as a source of new information for financial markets. By integrating multiple datasets from WRDS and applying an event-study methodology, this study evaluates the economic role of earnings disclosures in market efficiency, showcasing the valuation purpose of accounting. The integration of multiple databases adds complexity, requiring a detailed understanding of their structures and careful scripting to extract, align, and analyze data effectively. Key tasks include replicating and comparing original results, extending the analysis to data from 2007–2023, and applying the methodology to a non-U.S. country to explore cross-market variations.

@@

Earnings announcements provide investors with valuable information about a firm’s market value, with stock prices reacting significantly when earnings news deviates from expectations [@fink_review_2021, p.2]. The seminal study by @ball_empirical_1968 was the first to document this relationship, showing that stock prices anticipate earnings surprises, with most of the market reaction occurring before the official announcement, suggesting that earnings reports primarily confirm rather than introduce new information. Over the past decades, more than a thousand studies have examined the interplay between capital markets and financial statements, a research stream that originated with Ball and Brown (1968)  [@kothari_capital_2001]. This reinforces the role of earnings announcements as a crucial source of financial information.

@@

# Task 1 - Replication of Key Tables and Figures {#sec-task1}

@@

# Task 2 - Extending the Analysis to 2007–2023 {#sec-task2}

# Task 3 - Cross-Country Replication {#sec-task3}

# Task 4 - Research Design for a Non-Archival Study {#sec-task4}
